Ecological network control

### 2018-05-21 paper/supp-info.Rmd
Add figure maximum matching to supp info

## Finding a single maximum matching {#one-maximum-matching}

>>>>

## Finding a single maximum matching {#one-maximum-matching}
```{r}
drake::loadd(fig_supp_matching)
```

```{r fig-maximum-matching-procedure, fig.height=fig_supp_matching$height, fig.width=fig_supp_matching$width,fig.cap = "Finding a maximum matching in a complex network. (left) Directed network that indicate the direction of control between species. (center) Alternative bipartite representations of the directed networks. (right) The matchings in the bipartite representation mapped back to the original network."}
replayPlot(fig_supp_matching$plot)
```
